Bioverse: Origins of Life

### 2024-06-20 src/tex/ms.tex
elaborate and specify Bioverse's application here

\subsection{Exoplanet survey simulations with Bioverse}
To model the sensitivity of the information gain of a proposed mission to sample selection and survey strategy, we now conduct survey simulations with Bioverse using different sample sizes and survey strategies.
We again require that life occurs only on planets with sufficient past UV irradiation exceeding $F_\mathrm{NUV, min}$.
Further, we require this flux to have lasted for a minimum duration $\Delta T_\mathrm{min}$ to allow for a sufficient ``origins timescale''~\citep{Rimmer2023}.

All common Origin of Life scenarios require water as a solvent.
We thus consider only rocky planets that may sustain liquid water on their surface, i.e., that occupy their momentary \gls{HZ} during the above period.

\subsubsection{Habitable zone occupancy and UV flux}
Different formulations of habitable zones as regions around a star where a planet with Earth's atmospheric composition can maintain liquid water on its surface exist~\citep[e.g.,][]{MolLous2022,Spinelli2023,Tuchow2023}. CITE! Ramirez \& Kaltenegger 2017, 2018
Here, we adopt the popular estimates of \citet{Kasting1993} and \citet{Kopparapu2013,Kopparapu2014} that define a temperate zone between the runaway greenhouse transition CITE! and the maximum greenhouse limit CITE!.
We use the parametrization in \citet{Kopparapu2014} to derive luminosity and planetary mass-dependent edges of the \gls{HZ} $a_\mathrm{inner}$ and $a_\mathrm{outer}$.
We further follow \citet{Bixel2021} and classify as \glspl{EEC} all planets with radii $0.8 S^{0.25} < R < 1.4 $ that orbit within the above boundaries.
The lower limit was suggested as a minimum planet size to retain an atmosphere~\citep{Zahnle2017}.

>>>>

\subsection{Exoplanet survey simulations with Bioverse}
To assess the information gain of a real exoplanet survey, we employed Bioverse~\citep{Bixel2021}, a framework that integrates multiple components including statistically realistic simulations of exoplanet populations, a survey simulation module, and a Bayesian hypothesis testing module to evaluate the statistical power of different observational strategies.
The general approach is as follows:
\begin{enumerate}
\item \textbf{Exoplanet population synthesis:} We populate the Gaia Catalogue of Nearby Stars~\citep{Smart2021} with synthetic exoplanets whose orbital parameters and planetary properties reflect our current understanding of exoplanet demographics~\citep{Bergsten2022}.
    \item \textbf{Survey simulation:} We simulate the detection and characterization of these exoplanets with a hypothetical survey, taking into account the survey's sensitivity, target selection, and observational biases.
To model the sensitivity of the information gain of a proposed mission to sample selection and survey strategy, we conduct survey simulations with Bioverse using different sample sizes and survey strategies.
    \item \textbf{Hypothesis testing:} We employ Bayesian statistical methods to evaluate the likelihood that a given survey would detect a specified statistical trend in the exoplanet population and estimate the precision with which the survey could constrain the parameters of that trend.
    A common definition of the null hypothesis $H_0$, which is also applied here, is that there is no relationship between the independent variable (here: maximum NUV flux) and the dependent variable (here: biosignature occurrence).
    The alternative hypothesis $H_1$ proposes a specific relationship parameterized by $\theta$.
    If the dependent variable is of binary nature such as in the case of biosignature detections, we model the likelihood function as
    \begin{equation}
\mathcal{L}(y \mid \boldsymbol{\theta})=\prod_i^N\left[y_i h\left(\boldsymbol{\theta}, x_i\right)+\left(1-y_i\right)\left(1-h\left(\boldsymbol{\theta}, x_i\right)\right)\right],
\end{equation}
where here $y_i \in \{0,1\}$ is the biosignature detection variable, $x_i$ is the maximum NUV flux, and $h(\boldsymbol{\theta}, x_i)$ is the probability of detecting a biosignature given the maximum NUV flux and the model parameters $\boldsymbol{\theta}$.
We then use a nested sampling method~\citep{Speagle2020} to compute the Bayesian evidence for the null and alternative hypotheses and estimate the strength of evidence for the alternative hypothesis.

To determine the diagnostic capability of a given survey, Bioverse runs multiple iterations of the simulated survey and calculates the fraction of realizations that successfully reject the null hypothesis.
We use this metric, known as the statistical power, to quantify the potential information content of the survey, identify critical design trades, and find strategies that maximize the survey's scientific return.
The posterior samples obtained from the nested sampling runs further allows us to estimate the precision with which the survey could constrain the parameters of the hypothesized trend.
\end{enumerate}

\subsubsection{Habitable zone occupancy and UV flux}
To test the UV hypothesis, we require that life occurs only on planets with sufficient past UV irradiation exceeding $F_\mathrm{NUV, min}$.
Further, we require this flux to have lasted for a minimum duration $\Delta T_\mathrm{min}$ to allow for a sufficient ``origins timescale''~\citep{Rimmer2023}.
All common Origin of Life scenarios require water as a solvent;
we thus consider only rocky planets that may sustain liquid water on their surface, i.e., that occupy their momentary \gls{HZ} during the above period.

Different formulations of habitable zones as regions around a star where a planet with Earth's atmospheric composition can maintain liquid water on its surface exist~\citep[e.g.,][]{MolLous2022,Spinelli2023,Tuchow2023}. CITE! Ramirez \& Kaltenegger 2017, 2018
Here, we adopt the popular estimates of \citet{Kasting1993} and \citet{Kopparapu2013,Kopparapu2014} that define a temperate zone between the runaway greenhouse transition CITE! and the maximum greenhouse limit CITE!.
We use the parametrization in \citet{Kopparapu2014} to derive luminosity and planetary mass-dependent edges of the \gls{HZ} $a_\mathrm{inner}$ and $a_\mathrm{outer}$.
We further follow \citet{Bixel2021} and classify as \glspl{EEC} all planets with radii $0.8 S^{0.25} < R < 1.4 $ that orbit within the above boundaries.
The lower limit was suggested as a minimum planet size to retain an atmosphere~\citep{Zahnle2017}.
